Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling

### 2020-06-29 ans_to_reviewers/answers-to-reviewers.tex

\maketitle

We are grateful to the editors and reviewers for their comments and
suggestions. They have all been considered in this revised
version of our manuscript. We have worked a lot on developing both theoretical results, computational resources, and on the paper presentation. To help us in these efforts, we included Cedric Travelletti as co-author because he has contributed significantly on the revised version of the paper. \\

The principal revisions made to the manuscript are as shown in this list, and they are done to address the main comments of Editors and Reviewers:

\begin{enumerate}
\item The revision has lead to {\bf{structural changes}} as follows: \\
    i) Section 1 and 2 are now combined into one single \emph{Introduction} which should help the narrative and highlight the main contributions of the work. \\
    ii) The data assimilation part is now merged with equations for co-Kriging to clarify that this work is on multivariate GRFs. \\
    iii) Split the simulation study in two and used these as to directly motivate the statistical concepts of uncertainty reduction (Sect 2) and adaptive sampling strategies (Sect 3).
    iv) Present mathematical contributions succinctly in Section 2 and 3, while the mathematical proofs are in Appendix.

\item The motivation for excursion sets (ESs), and in particular that of {\bf{multivariate ESs}}, has been strengthened in this revision. Motivating examples are abundant in medicine where doctors do not solely rely on a single symptom but must see several combined effects before making a diagnosis, for example. Our motivation in the current paper is that temperature and salinity are proxies/indicators for more complex biological variables in the ocean, and in several cases they must be jointly high or low for phenomena to occur.

@@

In the revised manuscript these aspects are largely rewritten, in particular in the Introduction. \\
This change addresses comments of Associate Editor and Rev. 1 in particular.

\item The {\bf{statistical methodological contribution}} have been clarified and improved, including definitions of random sets and ESs. This also includes more general results than previously which just included the EIBV for the bi-variate case of temperature and salinity. The revised version highlights these novel statistical results as a main contribution of the paper. 
We emphasize the statistical design problem which is sought solved by the AUV with its constraints on navigation and computing resources.
In this sense, the revised version should provide ample motivation for statisticians, while still maintaining strong links to the application for illustrating concepts.

### 2020-06-29 cover_letter/cover_letter.tex
Updates from Overleaf

Please see our manuscript \textbf{Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets} submitted for possible publication in the \emph{Annals of Applied Statistics} (AOAS).\\*

This work focuses on tackling the challenges related to oceanographic sampling, where observations are expensive, few, and far apart. A key question in this regard is

\begin{quote}
\textit{where, when, and how should we gather information in order to effectively characterize a phenomenon in the ocean?}  
\end{quote}{}

The research presented aims to address this central question by combining statistical models and methodology with autonomous robotic sensing platforms. A central effort is the introduction of informative descriptions of spatial characteristics of ocean phenomena that greatly improve how sequential data collection can be conducted. Specifically, we present a design criterion based on reducing uncertainty in the joint excursions of random fields, and derive analytical expressions for the expected Bernoulli variance reduction in the excursion set of spatial temperature and salinity variables. The proposed methodology is deployed and tested in a full-scale deployment where an autonomous underwater vehicle is used to map a river plume.

This interdisciplinary study demonstrates the potential of statistics applied to support autonomous robotic decision making, representing methods and approaches with a substantial potential for further integration, which are necessary and critical to understand our changing oceans. 
\vspace{1em}

>>>>

We thank the editors and reviewers for providing feedback on our manuscript \textbf{AOAS1910-027}. The feedback have been insightful and constructive. Our response is attached along with the updated manuscript itself. We have carefully considered all the feedback in this revised version of the manuscript, which we believe is a significantly improved version of our work.

After extensive discussion we collectively felt the need to not only recruit an additional co-author, but also to change the title to 'Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling', which we believe better reflects the current manuscript and the valuable reviewer and editorial feedback.

We look forward to receiving any further feedback at the earliest.
\vspace{1em}
